Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-05 paper.qmd
Updated Figure 1 (c)

tsne_two_curvy_scaled <- algo_obj_two_curvy$nldr_scaled
distance_two_curvy <- algo_obj_two_curvy$distance_df
tr_from_to_df_two_curvy <- algo_obj_two_curvy$tr_from_to_df
benchmark_two_curvy <- algo_obj_two_curvy$benchmark
df_bin_centroids_two_curvy <- algo_obj_two_curvy$df_bin_centroids
df_bin_two_curvy <- algo_obj_two_curvy$df_bin
hex_grid_with_counts <- algo_obj_two_curvy$hex_grid_with_counts
hex_grid_nonempty <- algo_obj_two_curvy$hex_grid_nonempty
bin_width <- algo_obj_two_curvy$a1

@@

>>>>

tsne_two_curvy_scaled <- algo_obj_two_curvy$nldr_scaled
tr_from_to_df_two_curvy <- algo_obj_two_curvy$tr_from_to_df
df_bin_centroids_two_curvy <- algo_obj_two_curvy$df_bin_centroids
df_bin_two_curvy <- algo_obj_two_curvy$df_bin
hex_grid_with_counts <- algo_obj_two_curvy$hex_grid_with_counts
hex_grid_nonempty <- algo_obj_two_curvy$hex_grid_nonempty
bin_width <- algo_obj_two_curvy$a1

@@

df_bin_centroids_two_curvy <- df_bin_centroids_two_curvy |>
  dplyr::filter(std_counts > 0)
